Compositional Equivalences Based on Open pNets

### 2022-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
vars

pNets are tree-like structures, where the leaves are either \emph{parameterised labelled transition systems (pLTSs)}, expressing the
behaviour of basic processes, or \emph{holes}, used as placeholders
for unknown processes. 
%, of which we only specify the set of possible
%actions, this set is named the \emph{sort}.
Nodes of the tree (pNet nodes) are synchronising artefacts, using a
set of \emph{synchronisation vectors} that express the possible
synchronisation between the parameterised actions of a subset of the sub-trees.

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes \qquad
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle$ \qquad
where:
\begin{itemize}
\item[$\bullet$] $I$ is a set of indices and $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

@@

\item The set of variables of a pNet $P$, denoted $vars(P)$ is disjoint union the set of variables of  all pLTSs that compose $P$.

@@

The initial state is defined as:
$InitState(\pNet) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
\end{definition}
To be precise, the state of each pLTS is entirely characterized by both the state of the automaton, and the value of its variables $V$. Consequently, the state of a pNet is not only characterized the tuple of pLTS states but also contains the value of its variables $vars(P)$.

>>>>

pNets are tree-like structures, where the leaves are either \emph{parameterised labelled transition systems (pLTSs)}, expressing the
behaviour of basic processes, or \emph{holes}, used as placeholders
for unknown processes. 
%, of which we only specify the set of possible
%actions, this set is named the \emph{sort}.
Every node of the tree  is a pNet, it acts as a  synchronising artefacts, using a
set of \emph{synchronisation vectors} that express the possible
synchronisation between the parameterised actions of a subset of the sub-trees.

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes 
\[
\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle\]
 We denote $\vars(P)$ the set of variables used by the pLTSs inside $P$ and $\Sort(P)$  the signature of the actions emitted by $P$; both are defined below, in Definition~\ref{def-sortholeleave}. A pNet is composed of the following:
\begin{itemize}
\item[$\bullet$] $I$ is a set of indices and $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $\vars(P_i)$ and $\vars(P_j)$ must be disjoint for $i\neq j$.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

@@

\item The set of variables of a pNet $P$, denoted $\vars(P)$ is disjoint union the set of variables of  all pLTSs that compose $P$.

@@

The initial state is defined as:
$InitState(\pNet) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
\end{definition}
To be precise, the state of each pLTS is entirely characterized by both the state of the automaton, and the value of its variables $V$. Consequently, the state of a pNet is not only characterized the tuple of pLTS states but also contains the value of its variables $\vars(P)$.
